\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Anurag Mishra} & Email: \href{mailto:anurag.mishra899n@gmail.com}{anurag.mishra899n@gmail.com} \\
  \href{https://medium.com/@anuragmishra_27746}{Medium: \@anuragmishra\_27746} & Mobile: +91-9456243057 \\
  \href{https://github.com/anurag-mishra899}{Github: github.com/anurag-mishra899} & \href{https://www.linkedin.com/in/anurag-mishra-660961b7/}{LinkedIn: Anurag Mishra} \\
\end{tabular*}


%--------Profile Summary---------------
\vspace{5pt}

\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Experience}{\textbf{6.5+ YoE} in designing and developing \textbf{Machine Learning, Deep Learning, Generative AI, and NLP} solutions for various industries, including retail, banking, telecommunications, and chemicals}
	\resumeSubItem{Frameworks}{PyTorch, Langchain, LlamaIndex, Fastapi, Scikit, NLTK, SpaCy, TensorFlow, Keras}
	\resumeSubItem{Tools}{Kubernetes, Docker, GIT, PostgreSQL, MySQL, SQLite}
	\resumeSubItem{Platforms}{Azure Cloud, AWS, GCP, Linux}
    \resumeSubItem{Certified in}{\textbf{Azure Fundamental, Azure Data Scientist, Databricks ML Professional}}
    \resumeSubItem{Publications}{\href{https://x.com/LangChainAI/status/1758895834077466825?t=bkoZkX7IcRj-6DsQ9DjfBw&s=19}{Article 1}, \href{https://medium.com/@anuragmishra_27746/five-levels-of-chunking-strategies-in-rag-notes-from-gregs-video-7b735895694d}{Article 2}, \href{https://medium.com/@anuragmishra_27746/optimizing-rags-overcoming-architecture-hurdles-for-peak-performance-part-1-8b5493b6a114}{Article 3}, \href{https://www.youtube.com/watch?v=lBOeELjndJo}{GenAI Conference}}
	\resumeSubHeadingListEnd

\vspace{5pt}

%--------Experience---------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{EY GDS}{Hybrid}{Associate Manager (Full-time)}{Feb 2022 - Present}
    \resumeItemListStart
        \resumeItem{Deployed GenAI Chat-bot Solution in Production}{
            \begin{itemize}
                \item Led \textbf{a team of 6 engineers} in designing and developing \textbf{Chat-bot solution for 2-3k users across 40 Branches} for Largest bank in Philippines.
                \item Built solution reduces time-spent manually from \textbf{5-10 min/query to $<$30 seconds.}
            \end{itemize}
            }
        \resumeItem{Developed LLM Production Pipeline}{
            \begin{itemize}  
                \item Implemented \textbf{custom prepossessing pipeline and chunking strategy} to handle \textbf{complex tables, pdf formatting \& flow-charts etc.}
                \item Build scalable deployment pipeline for using Fastapi, Langchain \& \href{https://github.com/Azure-Samples/AI-Gateway}{Azure API Gateway}, Kubernetes to \textbf{support throttling, fallbacks, load balancing to handle rate-limit, exceeded quota issues}.
            \end{itemize}     
            }
        \resumeItem{LLMOps \& Evaluation Pipeline}{
            \begin{itemize}
                \item Implemented custom RAG evaluation framework for \textbf{automated assessment for E2E RAG and individual components (routing, retrieval, generation etc)} to improve performance and optimize the solution. 
                \item Developed \textbf{monitoring pipeline using Langfuse} to observability and logging. Build Feedback Capturing mechanism to continuous enhancement of solution.
            \end{itemize}
        }
        \resumeItem{Smart Call Centre Solution for US Based Automotive Client}{
            \begin{itemize}
                \item Developed LLM \& data ingestion pipeline integrating Azure DevOps, Azure App Services, OpenAI models, Langchain \& integration with ServiceNow to manage Post-Call Actions, including call summarization, Ticket Creation \& Updates, categorization and Quality Assurance.
                \item Designed pipeline to handle 300-400 calls/centre which increase agent's productivity by 60\% in hourly-time spent.
            \end{itemize} }
        \resumeItem{Fine-tuning of Transformer-Based Models (BERT, RoBerta etc)}{
            \begin{itemize}
                \item Perform fine-tuning of transformer based models using Pytorch, hugging-face for downstream tasks i.e. NER \& Text Classification to build document extraction solution.
                \item Deployed deep learning models as batch endpoints utilizing Azure Web Apps, Databricks Jobs, and MLflow for streamlined integration and efficient model management.
            \end{itemize}}
        \resumeItem{Go-to-Market Strategy on Generative AI}{Involved in “Go to Market” strategy on Generative AI for various client and developed prototype on different industry use-cases using LLM models i.e. OpenAI, LlaMa, MPT, Dolly etc and took client awareness session on \href{https://shorturl.at/jsPSZ}{“Industry Implementation and Risks of GenAI”}}
      \resumeItemListEnd
\vspace{5pt}

    \resumeSubheading{Deloitte (Office of US)}{Remote}{Consultant - AI (Full-time)}{Feb 2021 - Feb 2022}
    \resumeItemListStart
        \resumeItem{Fixture Optimization for Inventory Management}{Devised optimization solution to allocate optimum number of fixtures for each product and brands for one of biggest global retail chain stores. The solution has provided \$5 million reduction in cost and expense.}
        \resumeItem{Custom Clustering Approach with Constraints}{Implemented clustering and optimization algorithms to assign the optimum fixtures, while keeping up the various geographically and logistically business constraints.}
        \resumeItem{Sales Forecasting for Retail Client}{Performed Sales Forecasting model for each department per store to assess the demand. Utilized various Tree based algorithms e.g.- Gradient Boosting, XGBoost \& LightGBM and regression-based model e.g.- ARIMA, \& SARIMA for the prediction.}
        \resumeItem{Tools \& Technologies}{Used Python programming and worked with libraries such as Pandas, Scikit-learn, NumPy, Matplotlib, and Seaborn.}
      \resumeItemListEnd
\vspace{-3pt}
    \resumeSubheading{Virtusa Polaris}{Hybrid}{Machine Learning Engineer}{June 2018 - Feb 2021}
	\resumeItemListStart
        \resumeItem{Multi-Class classification of Trading Products}{Devised solution for Product Controllers to reduce person-hours spent on tasks of identifying breach in trading activity. Used multi-class classification and ETL operations to perform pre- and post-breach analysis.}
        \resumeItem{NLP Models to Assess Commentary using Spacy}{Developed NLP solution to identify the inconsistency in PnL commentary generated by Product Controllers. Milestones included building RestAPI to render user request and ETL operations to handle user requests.}
        \resumeItem{Impact}{Built solutions has increased the numbers of tagging 15k /hour to 1 million /hour}
        \resumeItem{ML Models/Approaches}{Implemented various ML algorithms like Random Forest, Logistic regression, Support Vector Machine, Gradient Boosting and parameter tuning the model for the optimum solution }
        \resumeItem{Tools \& Technologies}{Used Python programming and worked on libraries like Pandas, Scikit-learn, NumPy, Matplotlib, Seaborn, Spacy}
	\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Fine-Tuned LLM for Domain Specific tasks using LoRA}{Performed Fine-tuning of LLM models(llama 3.1 8B, mistral 7B) on 80 GB A-100 GPU on custom build dataset for Manufacturing domain.}
\vspace{2pt}
\resumeSubItem{LLM Based Agentic flow for Text to Code Solution}{Agent based solution that convert requirements to code. The solution uses multi-agents (debugger, coder, tester etc) to write the bug-free and optimized code.}
\vspace{2pt}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute of Technology, Manipur}{India}
      {Bachelor of Technology - Information Technology; GPA: 8.5}{July 2014 - June 2018}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Networking, Databases}}}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Honors and Awards}
\resumeSubHeadingListStart
  \item {Awarded Excellence Client Performance Award in EY}
  \item {Honoured to be among in top 10 students in CSE Department}
  \item {Achieved (Among Top 1 \% in board) in Entire district in HSC exam.}
\resumeSubHeadingListEnd

%-----------VOLUNTEER EXPERIENCE-----------------
%\section{Volunteer Experience}
%  \resumeSubHeadingListStart
%	\resumeSubheading
%    {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}{Conducted technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
%	\resumeSubheading
%    {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}{Organized events, workshops, reaching over 7000 people.}{Nov 2017 - Present}
%\resumeSubHeadingListEnd

\end{document}
